\subsection*{CHANGELOG}

\begin{tabularx}{\textwidth}{@{} >{\raggedleft}p{2.25cm} | X @{}}
  Aug 2020 & \primary{Senior Software Engineer} \at \href{https://onfido.com/}{\secondary{Onfido}} \tertiary{(London, UK)} \\
- Present  & \tbullet Working across multiple backend services to help analyze, detect and
             prevent frauds at scale in tens of millions of end-user records per month,
             involving data pipeline, event-driven architecture and system scaling \& monitoring. \\
           & \tbullet Contributed to improving image \& video capture experience and quality for the Onfido Web SDK
             that helped reduce drop-off by 5-10\% and increase pass rate by 10-30\%. \\
  \\
  Sep 2019 & \primary{Senior Software Engineer} \at \href{https://www.pi-top.com/}{\secondary{Pi-top}} \tertiary{(UK Remote)} \\
- Jul 2020 & \tbullet Developed new features in both backend and frontend for Further, a learning-by- \\
     (11m) & making platform on top of Raspberry Pi hardware devices. \\
           & \tbullet Worked with stakeholders to clarify requirements from thousands of teachers and students in North America and Europe. \\
           & \tbullet Contributed to improving the project's structure and performance, as well as the team's work process. \\
  \\
  Aug 2016 & \primary{Senior Software Engineer} \at \href{https://youtu.be/_FhxbwNqGS8}{\secondary{WeFit}} \tertiary{(Hanoi, Vietnam)} \\
- Aug 2019 & \tbullet In charge of the architecture and the design of WeFit mobile application, an online-to- \\
      (3y) & offline platform which connects users and local fitness studios, serving 200,000+ users with 2000+ DAUs. \\
           & \tbullet Built web-based tools which manage 10,000+ user bookings and revenues for 300+ fitness partners monthly. \\
  \\
  Aug 2014 & \primary{Dev Lead} \then \primary{Head of Operations} \at \href{https://topica.asia/}{\secondary{TOPICA Edtech Group}} \tertiary{(Hanoi, Vietnam)} \\
- Aug 2016 & \tbullet Managed Operations department of 30 to connect 200+ instructors and create 500+ \\
   (2y 1m) & video courses for Edumall, a short-course learning platform. \\
           & \tbullet Led development team of 10 to build and launch Web, iOS and Android applications for Memo,
           an English learning product, serving 150,000+ users with 3000+ DAUs. \\
  \\
  Aug 2012 & \primary{Mobile Developer} \then \primary{Dev Lead} \at \href{https://vinova.sg/}{\secondary{Vinova Pte. Ltd.}} \tertiary{(Hanoi, Vietnam)} \\
- Sep 2014 & \tbullet Led a team of 3 to develop 5 different mobile applications for Singapore marketplace. \\
   (2y 2m) & \tbullet Advised customers on choosing proper technical stacks and decisions, maintained and upgraded the products on request. \\
  \\
  Aug 2009 & \primary{Undergrad} \at \href{https://e.uet.vnu.edu.vn}{\secondary{Vietnam National University, Hanoi}} \tertiary{(Hanoi, Vietnam)} \\
- May 2013 & Bachelor's Degree, Computer Science. \\
\end{tabularx}
