\newcommand{\primary}[1]{\textcolor{primary}{\textbf{#1}}}
\newcommand{\secondary}[1]{\textcolor{secondary}{\textbf{#1}}}
\newcommand{\tertiary}[1]{\textcolor{tertiary}{#1}}

\newcommand{\tbullet}{\textcolor{tertiary}{\textbf{$\bullet$}}\space}
\newcommand{\at}{\textcolor{tertiary}{\textbf{@}}\space}
\newcommand{\then}{\textcolor{tertiary}{$\Rightarrow$}\space}

\newcommand{\keybase}{\textcolor{secondary}{\href{https://keybase.io/ethan605}{\faKey}}}
\newcommand{\github}{\textcolor{secondary}{\href{https://github.com/ethan605}{\faGithub}}}
\newcommand{\linkedin}{\textcolor{secondary}{\href{https://linkedin.com/in/ethan605}{\faLinkedin}}}

\pagestyle{empty}

\begin{document}
\setlength\parindent{0pt}
\pagecolor{background}
\color{foreground}

\begin{center}
  \textcolor{primary}{\LARGE\bfseries\scshape{Thanh (Ethan) Nguyen}}
\end{center}

\begin{tabularx}{\textwidth}{
    @{}
    >{\raggedright\arraybackslash}X
    c
    >{\raggedleft\arraybackslash}X
    @{}
  }
  \href{mailto:xtnguyen605@gmail.com}{\textcolor{secondary}{xtnguyen605@gmail.com}} &
    \keybase \space \github \space \linkedin &
    \href{https://ethanify.me}{\textcolor{secondary}{ethanify.me}} \\
  \href{tel:447546634543}{(+44) 7546 634 543} & &
    London, UK \\
\end{tabularx}

\begin{spacing}{0.05}
\rule{\textwidth}{1pt} \\
\rule{\textwidth}{1pt}
\end{spacing}

\subsection*{SYNOPSIS}

Passionate about creating awesome products that help plenty of people improving their lives. \\
10+ years of experience in the software industry, mostly tech start-ups. \\
Speaking \textbf{Elixir}, \textbf{Python}, \textbf{Ruby on Rails} \& \textbf{TypeScript}. \\
Interested in \textbf{Rust}, \textbf{Go} \& \textbf{WebAssembly}.

\subsection*{CHANGELOG}

\begin{tabularx}{\textwidth}{@{} >{\raggedleft}p{2.25cm} | X @{}}
  Aug 2020 & \primary{Senior Software Engineer} \at \href{https://onfido.com/}{\secondary{Onfido}} \tertiary{(London, UK)} \\
- Present  & \tbullet Contributed to improving image \& video capture experience and quality for the Onfido Web SDK
             that helped reduce drop-off by 5-10\% and increase pass rate by 10-30\%. \\
           & \tbullet Working across multiple backend services to help analyze, detect and
             prevent frauds at scale in tens of millions of end-user records per month,
             involving data pipeline, event-driven architecture and system scaling \& monitoring. \\
  \\
  Sep 2019 & \primary{Senior Software Engineer} \at \href{https://www.pi-top.com/}{\secondary{Pi-top}} \tertiary{(UK Remote)} \\
- Jul 2020 & \tbullet Developed new features in both backend and frontend for Further, a learning-by- \\
     (11m) & making platform on top of Raspberry Pi hardware devices. \\
           & \tbullet Worked with stakeholders to clarify requirements from thousands of teachers and students in North America and Europe. \\
           & \tbullet Contributed to improving the project's structure and performance, as well as the team's work process. \\
  \\
  Aug 2016 & \primary{Senior Software Engineer} \at \href{https://youtu.be/_FhxbwNqGS8}{\secondary{WeFit}} \tertiary{(Hanoi, Vietnam)} \\
- Aug 2019 & \tbullet In charge of the architecture and the design of WeFit mobile application, an online-to- \\
      (3y) & offline platform which connects users and local fitness studios, serving 200,000+ users with 2000+ DAUs. \\
           & \tbullet Built web-based tools which manage 10,000+ user bookings and revenues for 300+ fitness partners monthly. \\
  \\
  Aug 2014 & \primary{Dev Lead} \then \primary{Head of Operations} \at \href{https://topica.asia/}{\secondary{TOPICA Edtech Group}} \tertiary{(Hanoi, Vietnam)} \\
- Aug 2016 & \tbullet Managed Operations department of 30 to connect 200+ instructors and create 500+ \\
   (2y 1m) & video courses for Edumall, a short-course learning platform. \\
           & \tbullet Led development team of 10 to build and launch Web, iOS and Android applications for Memo,
           an English learning product, serving 150,000+ users with 3000+ DAUs. \\
  \\
  Aug 2012 & \primary{Mobile Developer} \then \primary{Dev Lead} \at \href{https://vinova.sg/}{\secondary{Vinova Pte. Ltd.}} \tertiary{(Hanoi, Vietnam)} \\
- Sep 2014 & \tbullet Led a team of 3 to develop 5 different mobile applications for Singapore marketplace. \\
   (2y 2m) & \tbullet Advised customers on choosing proper technical stacks and decisions, maintained and upgraded the products on request. \\
  \\
  Aug 2009 & \primary{Undergrad} \at \href{https://e.uet.vnu.edu.vn}{\secondary{Vietnam National University, Hanoi}} \tertiary{(Hanoi, Vietnam)} \\
- May 2013 & Bachelor's Degree, Computer Science. \\
\end{tabularx}

\subsection*{VERSION \normalsize\texttt{2023.apr.10}}

\end{document}
