\subsection*{EXPERIENCE}

\begin{workexp}
  \primary{Senior Software Engineer} \at \href{https://onfido.com/}{\secondary{Onfido}} \tertiary{(London, UK)} &
  Aug 2020 - Present
\end{workexp}

\tbullet Working across multiple backend services to help analyze, detect and prevent frauds at scale in tens of millions of end-user records per month, involving data pipeline, event-driven architecture and system scaling \& monitoring. \newline
\tbullet Contributed to improving image \& video capture experience and quality for the Onfido Web SDK that helped reduce drop-off by 5-10\% and increase pass rate by 10-30\%. \newline

\begin{workexp}
  \primary{Senior Software Engineer} \at \href{https://www.pi-top.com/}{\secondary{Pi-top}} \tertiary{(Remote)} &
  Sep 2019 - Jul 2020 \tertiary{(11mo)}
\end{workexp}

\tbullet Developed new features in both backend and frontend for Further, a learning-by-making platform on top of Raspberry Pi hardware devices. \newline
\tbullet Worked with stakeholders to clarify requirements from thousands of teachers and students in North America and Europe. \newline
\tbullet Contributed to improving the project's structure and performance, as well as the team's work process. \newline

\begin{workexp}
  \primary{Senior Software Engineer} \at \href{https://youtu.be/_FhxbwNqGS8}{\secondary{WeFit}} \tertiary{(Hanoi, Vietnam)} &
  Aug 2016 - Aug 2019 \tertiary{(3yr)}
\end{workexp}

\tbullet In charge of the architecture and the design of WeFit mobile application, an online-to-offline platform which connects users and local fitness studios, serving 200,000+ users with 2000+ DAUs. \newline
\tbullet Built web-based tools which manage 10,000+ user bookings and revenues for 300+ fitness partners monthly. \newline

\begin{workexp}
  \primary{Dev Lead} \at \href{https://topica.asia/}{\secondary{TOPICA Edtech Group}} \tertiary{(Hanoi, Vietnam)} &
  Aug 2014 - Aug 2016 \tertiary{(2yr 1mo)}
\end{workexp}

\tbullet Managed Operations department of 30 to connect 200+ instructors and create 500+ video courses for Edumall, a short-course learning platform. \newline
\tbullet Led development team of 10 to build and launch Web, iOS and Android applications for Memo, an English learning product, serving 150,000+ users with 3000+ DAUs. \newline

\begin{workexp}
  \primary{Mobile Developer} \at \href{https://vinova.sg/}{\secondary{Vinova Pte. Ltd.}} \tertiary{(Hanoi, Vietnam)} &
  Aug 2012 - Sep 2014 \tertiary{(2yr 2mo)}
\end{workexp}

\tbullet Led a team of 3 to develop 5 different mobile applications for Singapore marketplace. \newline
\tbullet Advised customers on choosing proper technical stacks and decisions, maintained and upgraded the products on request. \newline

\begin{workexp}
  \primary{Undergrad} \at \href{https://e.uet.vnu.edu.vn}{\secondary{Vietnam National University, Hanoi}} &
  Aug 2009 - May 2013 \tertiary{(3yr 10mo)}
\end{workexp}

\tbullet Bachelor's Degree, Computer Science.
