\subsection*{EXPERIENCE}

\WorkExp{Senior Software Engineer}{https://encord.com/}{Encord}{(London, UK)}
  {Apr 2024 - Present}

\WorkDesc{
  \item Led ``Enterprise Readiness'' initiatives to implement foundational features for enterprise customers,
  including but not limited to IAM (Identity and Access Management), user lifecycle \& resource management,
  customer experience \& scalability, and on-premise and VPC deployments.
  \item Smoothly onboarded enterprise customers with higher ACV and contributed to overall ARR increment.

  \item \tertiary{Skills}: FastAPI, PostgreSQL, SQLAlchemy, GCP, Kubernetes, RabbitMQ, TypeScript, React.js.
}

\WorkExp{Senior Software Engineer}{https://orca.security/}{Orca Security}{(London, UK)}
  {June 2023 - Feb 2024 \tertiary{(9mo)}}

\WorkDesc{
  \item Contributed to building solutions based on Graph Database (using Apache TinkerPop \& Gremlin) as part of
  Context Analysis team, which is a foundational building block for Cloud Security Analysis.

  \item \tertiary{Skills}: Python (Django), AWS, Kubernetes, PostgreSQL, AWS Neptune \& Apache TinkerPop.
}

\WorkExp{Senior Software Engineer}{https://onfido.com/}{Onfido}{(London, UK)}
  {Aug 2020 - June 2023 \tertiary{(2yr 11mo)}}

\WorkDesc{
  \item Collaborated on various backend services to tackle fraud analysis, detection, and prevention at a large scale,
  handling tens of millions of end-user records monthly. Involved in designing data pipelines,
  event-driven architecture, and system scaling and monitoring.

  \item Played a key role in enhancing the image and video capture experience and quality for the Onfido Web SDK.
  This improvement led to a 5-10\% reduction in drop-off rates and a 10-30\% increase in pass rates.

  \item \tertiary{Skills}: Python (Flask), Ruby on Rails, Elixir, AWS, Kubernetes, PostgreSQL, React.js \& TypeScript.
}

\WorkExp{Senior Software Engineer}{https://www.pi-top.com/}{Pi-top}{Remote}
  {Sep 2019 - Jul 2020 \tertiary{(11mo)}}

\WorkDesc{
  \item Developed new features in both backend and frontend (using React \& Redux) for Further, a learning-by-making
  platform on top of Raspberry Pi hardware devices.

  \item Collaborated with stakeholders to clarify requirements from thousands of teachers and students in
  North America and Europe, contributing to the improvement of project structure, performance, and team work process.

  \item \tertiary{Skills}: Python, TypeScript (Loopback.js), GCP, Kubernetes, MongoDB, React.js \& GraphQL.
}

\WorkExp{Senior Software Engineer}{https://youtu.be/_FhxbwNqGS8}{WeFit}{(Hanoi, Vietnam)}
  {Aug 2016 - Aug 2019 \tertiary{(3yr)}}

\WorkDesc{
  \item Led the architecture and design of the WeFit mobile application, an online-to-offline platform connecting
  users with local fitness studios. Successfully served over 200,000 users with 2000+ daily active users.

  \item Developed robust web-based tools to efficiently manage a high volume of user bookings and revenues,
  supporting 10,000+ bookings and working with 300+ fitness partners on a monthly basis.

  \item \tertiary{Skills}: TypeScript, Ruby on Rails, Python, PostgreSQL, React.js, Next.js \& React Native.
}

\WorkExp{Dev Lead}{https://topica.asia/}{TOPICA Edtech Group}{(Hanoi, Vietnam)}
  {Aug 2014 - Aug 2016 \tertiary{(2yr 1mo)}}

\WorkDesc{
  \item Oversaw the Operations department of 30 members, facilitating seamless collaboration between 200+ instructors
  to curate and deliver 500+ video courses on Edumall, a prominent short-course learning platform.

  \item Spearheaded a talented development team of 10 individuals, successfully delivering and launching Web, iOS,
  and Android applications for Memo, an innovative English learning product. Empowered over 150,000 users,
  achieving a daily active user base of 3000+.

  \item \tertiary{Skills}: Ruby on Rails, MongoDB, Objective-C, Swift.
}

\WorkExp{Mobile Developer}{https://vinova.sg/}{Vinova Pte. Ltd.}{(Hanoi, Vietnam)}
  {Aug 2012 - Sep 2014 \tertiary{(2yr 2mo)}}

\WorkDesc{
  \item Successfully led a team of 3 in the development of 5 diverse mobile applications catering to the
  Singapore marketplace.

  \item Demonstrated expertise in providing valuable technical guidance to customers, facilitating
  optimal technology selections, and taking proactive measures to maintain and upgrade products.

  \item \tertiary{Skills}: Objective-C, C++, iOS.
}

\WorkExp{Undergrad}{https://e.uet.vnu.edu.vn}{Vietnam National University, Hanoi}{}
  {Aug 2009 - May 2013 \tertiary{(3yr 10mo)}}

\WorkDesc{
  \item Bachelor's Degree, Computer Science.
}
